Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
getwd()
setwd("C:\\Users\\ares han\\Documents\\Learning\\Udacity\\R\\ExploreOneVariable")
getwd()
pf <- read.csv("pseudo_facebook.tsv", sep = '\t')
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
install.packages('ggplot2')
library(ggplot2)
names(pf) 
ggplot(data = pf, aes(x = dob_day, stat = "count")) + geom_bar() + scale_x_continuous(breaks = 1:31)
```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
ggplot(data = pf, aes(x = dob_day)) + 
  geom_histogram(binwidth = 1) + 
  scale_x_continuous(breaks = 1:31) + 
  facet_wrap(~dob_month)
```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
ggplot(data = pf, aes(x = friend_count)) + geom_bar()
```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram() + 
  scale_x_continuous(limits = c(0, 1000))
```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))

ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram(binwidth = 25) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 250))

ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram(binwidth = 25) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 250)) + 
  facet_wrap(~gender)
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
ggplot(aes(x = friend_count), data = subset(pf, !is.na(gender))) + 
  geom_histogram() + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  facet_wrap(~gender)
```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
table(pf$gender)
by(pf$friend_count, pf$gender, summary)
```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
Notes:

```{r Tenure}

```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
ggplot(aes(x = tenure), data = pf) + 
   geom_histogram(binwidth = 30, color = 'black', fill = '#099DD9')
```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
ggplot(aes(x = tenure / 365), data = pf) + 
  geom_histogram(color = 'black', fill = '#F79420') + 
  scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7)) + 
  xlab('Number of years using Facebook') + 
  ylab('Number of users in sample')
```

***

### User Ages
Notes:

```{r User Ages}
names(pf)
ggplot(aes(x = age ), data = pf) + 
  geom_histogram(color = 'black', fill = '#F79420') + 
  scale_x_continuous(breaks = seq(1, 120, 10), limits = c(0, 120)) + 
  xlab('Age of users using Facebook') + 
  ylab('Number of users in sample')
```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***
install.packages('gridExtra') 
library(gridExtra)
### Transforming Data
Notes:
myLog <- function(x) {
ifelse(abs(x) <= 1, 0, sign(x)*log10(abs(x)))
}

gg.friendcount <- ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram() 
gg.friendcountLog <- ggplot(aes(x = myLog(friend_count)), data = pf) + 
  geom_histogram() 
gg.friendcountSqrt <- ggplot(aes(x = sqrt(friend_count)), data = pf) + 
  geom_histogram() 
grid.arrange(gg.friendcount, gg.friendcountLog,gg.friendcountSqrt , ncol=3)
***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}
gg.friendcountLog1 <- ggplot(aes(x = myLog(friend_count)), data = pf) + 
  geom_histogram() 
gg.friendcountLog2 <- ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram() + scale_x_log10()
grid.arrange(gg.friendcountLog1,gg.friendcountLog2 , ncol=2)
```

***


### Frequency Polygons

```{r Frequency Polygons}
ggplot(aes(x = friend_count, y = ..count../sum(..count..)), data = subset(pf, !is.na(gender))) +
  geom_freqpoly(aes(color = gender), binwidth=10) + 
  scale_x_continuous(limits = c(100, 2000), breaks = seq(100, 2000, 50)) + 
  xlab('Friend Count') + 
  ylab('Percentage of users with that friend count')

```{Note that sum(..count..) will sum across color, so the percentages ```displayed are percentages of total users. To plot percentages within each ```group, you can try y = ..density...}

ggplot(aes(x = friend_count, y = ..density..), data = subset(pf, !is.na(gender))) +
  geom_freqpoly(aes(color = gender), binwidth=10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + 
  xlab('Friend Count') + 
  ylab('Percentage of users with that friend count')

ggplot(aes(x = www_likes), data = subset(pf, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender)) + 
  scale_x_log10()


```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
by(pf$www_likes,pf$gender, sum)
```


***

### Box Plots
Notes:

```{r Box Plots}
ggplot(aes(x = gender, y = friend_count), data = subset(pf, !is.na(gender))) + 
  geom_boxplot() + 
  scale_y_continuous(limits = c(0, 500), breaks = seq(0, 500, 50))  
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}

```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}

```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}
pf$mobile_check_in <- ifelse(pf$mobile_likes > 0, 1, 0)
pf$mobile_check_in <- factor(pf$mobile_check_in)
head(pf$mobile_check_in)
summary(pf$mobile_check_in)
sum(pf$mobile_check_in)/length
```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!