Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***
setwd("C:\\Users\\ares han\\Documents\\Learning\\Udacity\\R\\ExploreOneVariable")
pf <- read.csv("pseudo_facebook.tsv", sep = '\t')
install.packages("ggplot2")
install.packages("dplyr")
library(ggplot2)
library(dplyr)

### Scatterplots
Notes:

```{r Scatterplots}
ggplot(data = pf, aes(x = age, y = friend_count)) + geom_point()
```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(data = pf, aes(x = age, y = friend_count)) + geom_point() + xlim(13,90)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(data = pf, aes(x = age, y = friend_count)) + geom_point(alpha = 1/10) + xlim(13,90)
```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(data = pf, aes(x = age, y = friend_count)) + geom_point(alpha = 1/10) + xlim(13,90) +
  coord_trans( y = "sqrt")
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
names(pf)
ggplot(data = pf, aes(x = age, y = friendships_initiated)) + 
  geom_point(alpha = 1/10, position = position_jitter(h = 0)) +  
  xlim(13,90) + 
  coord_trans(y = "sqrt")

  
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
pf.fc_by_age <- pf%>%
  group_by(age) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(as.integer(friend_count)),
            n = n()) %>%
  arrange(age)

pf.fc_by_age 
```

Create your plot!

```{r Conditional Means Plot}

ggplot(data = pf.fc_by_age, aes(x = age, y = friend_count_mean)) + 
  geom_line(color = "red") +  
  geom_line(aes( y = friend_count_median),color = "blue", position = position_jitter(h = 0)) +  
  #geom_line(aes( y = n),color = "black", position = position_jitter(h = 0)) + 
  xlim(13,90) 
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(data = pf, aes(x= age, y = friend_count)) +
  coord_cartesian(xlim = c(13, 70), ylim = c(0,1000)) +
  geom_point(alpha = 0.5, position = position_jitter(h = 0), color = "orange") +
  geom_line(stat = "summary", fun.y = mean) + 
  geom_line(stat = "summary", fun.y = quantile, fun.args = list(probs = .9), linetype = 2, color = "blue") + 
  geom_line(stat = "summary", fun.y = quantile, fun.args = list(probs = .5), linetype = 2, color = "blue") + 
  geom_line(stat = "summary", fun.y = quantile, fun.args = list(probs = .1), linetype = 2, color = "blue")
  
```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor.test(pf$friend_count, pf$age)
with(pf, cor.test(age,friend_count))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf, age>=70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
names(pf)
ggplot(data=pf, aes(x = www_likes_received, y = likes_received  )) + 
   coord_cartesian(xlim = c(0, quantile(pf$www_likes_received,0.95)), ylim = c(0,7500)) + 
  geom_point(color = "orange") +
  geom_smooth(method = "lm", color = "red")


```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
with(pf, cor.test(www_likes_received,likes_received))
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
install.packages('car')
install.packages('pbkrtest')

library(alr3)
library(ggplot2)
data(Mitchell)
names(Mitchell)
```

Create your plot!

```{r Temp vs Month}
ggplot(data = Mitchell, aes(x = Temp, y = Month)) +
  geom_point()
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.
# 0
b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
with(Mitchell, cor.test(Temp, Month))
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
ggplot(aes(x=(Month%%12),y=Temp),data=Mitchell)+ 
  geom_point() 

install.packages("energy")
library(energy)

x <- seq(0, 4*pi, pi/20)
y <- cos(x)
qplot(x = x, y = y)
dcor.ttest(x, y)
cor.test(x, y)

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
names(pf)
head(pf)
```

***

### Age with Months Means

```{r Age with Months Means}
pf$age_with_months <- pf$age + (12 - pf$dob_month)/12
```

Programming Assignment
```{r Programming Assignment}
pf.fc_by_age_months <- pf%>% group_by(age_with_months) %>% 
  summarise(friend_count_mean = mean(friend_count),friend_count_median = median(friend_count),n = n()) %>%
  arrange(age_with_months)
pf.fc_by_age_months
```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}
ggplot(data = subset(pf.fc_by_age_months, age_with_months < 71), aes(x = age_with_months, y = friend_count_mean)) +
   geom_line()
```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

