---
title: "WhiteWineQuality"
author: "Song Han"
date: "2016-08-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{install necessary packages}
install.packages("ggplot2", dependencies = T) 
install.packages("knitr", dependencies = T)
install.packages("dplyr", dependencies = T)
install.packages("tidyr", dependencies = T)
install.packages('gridExtra') 
install.packages("GGally", dependencies = T)
install.packages('RColorBrewer')
install.packages("memisc")
install.packages("e1071")

```

## Load Library
```{load library}
library(ggplot2)
library(knitr)
library(dplyr)
library(tidyr)
library(gridExtra)
library(GGally)
library(RColorBrewer)
library(memisc)
library(e1071)
```

```{define fuction for RMSE}
rmse <- function(error)
{
  sqrt(mean(error^2))
}
```

```{load data}
setwd("C:\\Users\\ares\\Documents\\Udacity\\R\\EDA_Project")
WhiteWine <- read.csv("wineQualityWhites.csv", sep = ',')
WhiteWine <- tbl_df(WhiteWine)
WhiteWine$quality <- factor(WhiteWine$quality, levels = c("0","1","2","3","4","5","6","7", "8","9","10"))
WhiteWine_long <- WhiteWine %>% gather("variable","value",fixed.acidity: quality)
```

```{Initial inspections}
glimpse(WhiteWine)
summary(WhiteWine)
head(WhiteWine)
str(WhiteWine)
names(WhiteWine)
nrow(WhiteWine)
ncol(WhiteWine)
```

```{dispaly quality distribution}
ggplot(data = WhiteWine, aes(x = quality, stat = "count")) + geom_bar()
```

```{refine breaks for the distribution}
ggplot(data = WhiteWine, aes(x = quality, stat = "count")) + geom_bar()   + scale_x_continuous(breaks = 1:10) 
```

```{refine quality distribution by using converting count to log10}
ggplot(data = WhiteWine, aes(x = quality, stat = "count")) + geom_bar() +  scale_y_log10()  + scale_x_continuous(breaks = 1:10) 
```
using log scale cause missing observations because there are only 5 observations have quality 10  


```{check quality less than 3 or equals to 10}
WhiteWine %>% filter(quality <3 | quality == 10)  
```
There are 5 observations which quality equals to 10


```{Quality larger or equals  to 9}
WhiteWine_TopQuality <-  WhiteWine %>% filter(quality >= 9)  
```




```{check the distribution of other attributs}

gg.fixed.acidity <- ggplot(data = WhiteWine, aes(x = fixed.acidity, stat = "count")) + geom_histogram( binwidth = 1) +  scale_y_log10()   

gg.volatile.acidity <- ggplot(data = WhiteWine, aes(x = volatile.acidity, stat = "count")) + geom_histogram(  binwidth = 0.1) +  scale_y_log10()   

gg.citric.acid <- ggplot(data = WhiteWine, aes(x = citric.acid, stat = "count")) + geom_histogram( binwidth = 0.1) +  scale_y_log10()  

gg.residual.sugar <- ggplot(data = WhiteWine, aes(x = residual.sugar, stat = "count")) + geom_histogram(binwidth = 5) +  scale_y_log10()   

gg.chlorides <- ggplot(data = WhiteWine, aes(x = chlorides, stat = "count")) + geom_histogram(binwidth = 0.05) +  scale_y_log10()   

gg.free.sulfur.dioxide <- ggplot(data = WhiteWine, aes(x = free.sulfur.dioxide, stat = "count")) + geom_histogram(binwidth = 5) +  scale_y_log10()  

gg.total.sulfur.dioxide <- ggplot(data = WhiteWine, aes(x = total.sulfur.dioxide, stat = "count")) + geom_histogram(binwidth = 40) +  scale_y_log10()   

gg.density <- ggplot(data = WhiteWine, aes(x = density, stat = "count")) + geom_histogram(binwidth = 0.01) +  scale_y_log10()   

gg.pH <- ggplot(data = WhiteWine, aes(x = pH, stat = "count")) + geom_histogram(binwidth = 0.05) +  scale_y_log10()   

gg.sulphates <- ggplot(data = WhiteWine, aes(x = sulphates, stat = "count")) + geom_histogram(binwidth = 0.1) +  scale_y_log10() 

gg.alcohol <- ggplot(data = WhiteWine, aes(x = alcohol, stat = "count")) + geom_histogram(binwidth = 2) +  scale_y_log10()   

grid.arrange(gg.fixed.acidity, gg.volatile.acidity,gg.citric.acid
            ,gg.residual.sugar, gg.chlorides, gg.chlorides
            ,gg.free.sulfur.dioxide, gg.total.sulfur.dioxide, gg.density
            ,gg.pH, gg.sulphates, gg.alcohol, ncol=3)
```




```{use facet against a long dataset instead of create plots separately}
ggplot(data = WhiteWine_long, aes(x = value, stat = "count")) + geom_histogram(binwidth = 2)  + facet_grid(.~variable, scales = "free")+  scale_y_log10()

ggplot(data = WhiteWine_long, aes(x = value, stat = "count")) + geom_histogram()  + facet_wrap(~variable, scales = "free")+  scale_y_log10()

```

```{use ggally to glimpse}
ggpairs(data = WhiteWine,columns = 2:13,title = "White Wine Quanlity",colour = "set")

ncol(WhiteWine)

```

```{calculate correlation coefficient}
cor(WhiteWine)

```


```{check relationship between quality and alcohol}
ggplot(data = WhiteWine, aes(x = quality, y = alcohol,group = quality)) + geom_boxplot()

```

```{}
with(WhiteWine, cor.test(quality, alcohol))
with(WhiteWine, cor.test(quality, density))
factor(WhiteWine$quality)
ggplot(aes(x = density, y = alcohol, color = factor(quality)), data = WhiteWine) +  geom_point(alpha = 0.5, size = 1, position = 'jitter') + scale_color_brewer(type="seq", palette=1) +  
  ggtitle('Price (log10) by Cube-Root of Carat and Cut')


```

```{normalize attributes}
WhiteWine

 
doit <- function(x) {(x - min(x, na.rm=TRUE))/(max(x,na.rm=TRUE) -
min(x, na.rm=TRUE))}

WhiteWine$quality <- as.numeric(WhiteWine$quality)
WhiteWine_Normalized <- as.data.frame(lapply(WhiteWine[1:13], doit))
#head(WhiteWine_Normalized)
WhiteWine_Normalized$X <- WhiteWine$X
WhiteWine_Normalized$quality <- WhiteWine$quality
#head(WhiteWine_Normalized)
ggpairs(data = WhiteWine_Normalized,columns = 2:13
        ,title = "White Wine Quanlity")


```


```{Three Variables: alcohol, density, quality }
ggplot(WhiteWine,aes(x = alcohol, y = density, color = quality)) + 
  geom_point(alpha = 0.5, position = 'jitter') +
  scale_y_continuous(limits = c(0.985, 1.005)) +
  scale_color_brewer(type = 'seq', palette=3, guide = guide_legend(title = 'Quality', reverse = T,override.aes = list(alpha = 1, size = 2)))

ggplot(WhiteWine, aes(x=alcohol, fill=quality)) +
  geom_histogram(position="dodge", binwidth = 1) +
  scale_fill_brewer()
  
ggplot(WhiteWine, aes(x=density, fill=quality)) +
  geom_histogram(position="dodge", binwidth = 0.02) +
  scale_x_continuous(limits = c(0.985, 1.005)) + 
  scale_fill_brewer()
  
ggplot(WhiteWine, aes(x=chlorides, fill=quality)) +
  geom_histogram(position="dodge", binwidth = 0.02) +
  scale_x_continuous(limits = c(0.01, 0.1)) + 
  scale_fill_brewer()
```

```{4 variables}

ggplot(WhiteWine, aes(x=chlorides)) +
  geom_histogram(position="dodge") +
  scale_x_continuous(limits = c(0.01, 0.1), breaks = seq(0.01, 0.1, 0.005)) +
  scale_fill_brewer()
  
ggplot(WhiteWine,aes(x = alcohol, y = density, color = quality,size = chlorides)) + 
  geom_point(alpha = 0.5, position = 'jitter') +
  scale_y_continuous(limits = c(0.985, 1.005)) +
  scale_color_brewer(type = 'seq', palette=3, guide = guide_legend(title = 'Quality', reverse = T,override.aes = list(alpha = 1, size = 2)))+
  scale_size_area(limits = c(0.01, 0.1), breaks = seq(0.01, 0.1, 0.005))

ggplot(WhiteWine_Normalized,aes(x = alcohol, y = density, color = quality,size = chlorides)) + 
  geom_point(alpha = 0.5, position = 'jitter') +
  scale_color_brewer(type = 'seq', palette=3, guide = guide_legend(title = 'Quality', reverse = T,override.aes = list(alpha = 1, size = 2)))

```





```{linear regression model}
WhiteWine$quality <- as.numeric(WhiteWine$quality)


lm1 <- lm(quality ~ alcohol, data = WhiteWine)
lm2 <- update(lm1, ~ . + density)
lm3 <- update(lm2, ~ . + chlorides)
mtable(lm1, lm2, lm3)
mtable(lm1)
predictedY <- predict(lm3, WhiteWine)
lm3$residuals
error <- lm3$residuals  # same as data$Y - predictedY
predictionRMSE <- rmse(error)
predictionRMSE

data.frame(real = WhiteWine$quality, pred = predictedY)


plot(WhiteWine$alcohol,WhiteWine$quality )
abline(mbig1)
```

```{support vector machine}
WhiteWine$quality <- as.numeric(WhiteWine$quality)
svm1 <- svm(quality ~ alcohol, data = WhiteWine)
svm2 <- update(svm1, ~ . + density)
svm3 <- update(svm2, ~ . + chlorides)

predictedY_svm <- predict(svm3, WhiteWine)
error <- WhiteWine$quality - predictedY_svm
svrPredictionRMSE <- rmse(error)
svrPredictionRMSE 



svm(quality ~ .,  data = WhiteWine[,c("alcohol","density","chlorides","quality")])

tuneResult <- tune(svm, quality ~ .,  data = WhiteWine[,c("alcohol","density","chlorides","quality")],
                    ranges = list(epsilon = seq(0,1,0.1), cost = 2^(2:4)))
tuneResult



svm1 <- svm(quality ~ alcohol, data = WhiteWine)
svm2 <- update(svm1, ~ . + density)
svm3 <- update(svm2, ~ . + chlorides)

predictedY_svm <- predict(svm3, WhiteWine, epsilon = 0.3, cost = 6)
error <- WhiteWine$quality - predictedY_svm
svrPredictionRMSE <- rmse(error)
svrPredictionRMSE 

 0.7842435

- best parameters:
 epsilon cost
     0.3    4

```

- sampling method: 10-fold cross validation 



- best performance: 0.6133254 




## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
